---
title: "PvSeroApp in R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PvSeroApp_R_Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load the Package and Data

```{r setup 1}
library(SeroTrackR)
library(knitr)
library(rmarkdown)
library(tidyverse)

your_raw_data <- c(
  system.file("extdata", "example_MAGPIX_plate1.csv", package = "SeroTrackR"),
  system.file("extdata", "example_MAGPIX_plate2.csv", package = "SeroTrackR"), 
  system.file("extdata", "example_MAGPIX_plate3.csv", package = "SeroTrackR")
)
your_plate_layout <- system.file("extdata", "example_platelayout_1.xlsx", package = "SeroTrackR")
```

## Data Analysis: `runPvSeroPipeline()` 

Run this global function `runPvSeroPipeline()` embedded within the `{SeroTrackR}` R package! This function contains all of the steps in order of how to perform the *Plasmodium vivax* serology test and treat protocol as found in our [application](https://dionnecargy.shinyapps.io/PvSeroApp/)! 

### Run Classification: Yes {.tabset}

```{r runPvSeroPipeline with classification}
final_analysis <- runPvSeroPipeline(
  raw_data = your_raw_data, 
  plate_layout = your_plate_layout, 
  platform = "magpix", 
  location = "ETH", 
  experiment_name = "experiment1", 
  classify = "Yes", 
  algorithm_type = "antibody_model", 
  sens_spec = "maximised"
)

final_analysis
```

### Run Classification: No

```{r runPvSeroPipeline without classification}
no_classification_final_analysis <- runPvSeroPipeline(
  raw_data = your_raw_data, 
  plate_layout = your_plate_layout, 
  platform = "magpix", 
  location = "ETH", 
  experiment_name = "experiment1", 
  classify = "No", ########################## key if you do NOT want any classification performed i.e., you do not have PvSeroTaT antigens 
  algorithm_type = "antibody_model", 
  sens_spec = "maximised"
)
```

## Create a PDF Report

```{r create pdf output}
renderQCReport(
  your_raw_data, 
  your_plate_layout, 
  "magpix", 
  location = "ETH"
)
```
